Response to Pachter's Review

### 2020-01-22 index.Rmd
added excel

However, the empirical difference in citations was staggering and we could predict an objection. More professors from R2 (teaching focused universities) signed A, so it could have pushed the average down. We had already spent so much effort collecting Google Scholar citations, so we made a choice to only collect MathSciNet data on R1 Math Professors, which is why Professor Pachter did not have MathSciNet citations in our dataset. This choice was not made explicitly enough in our first version.  Let us look at the NaN values of those who are full math professors at R1 univesities.

@@

Pachter ends his review by saying "under-represented minorities and women routinely face discrimination and worse. This is completely unacceptable." We agree. But we do not believe that the solution is to allow for more diverse faculty regardless of their ability as researchers. What we do believe is that increasing opportunities for under represented minorities at an early stage and fairer hiring practices is the solution, not reverse discrimination [advocated by some](https://blogs.ams.org/inclusionexclusion/2017/05/11/get-out-the-way/).

>>>>

However, the empirical difference in citations was staggering and we could predict an objection. More professors from R2 (teaching focused universities) signed A, so it could have pushed the average down. We had already spent so much effort collecting Google Scholar citations, so we made a choice to only collect MathSciNet data on R1 Math Professors, which is why Professor Pachter did not have MathSciNet citations in our dataset. This choice was not made explicitly enough in our first version.  Let us look at the NaN values of those who are full math professors at R1 universities.

@@

Pachter ends his review by saying "under-represented minorities and women routinely face discrimination and worse. This is completely unacceptable." We agree. We believe that increasing opportunities for under represented minorities at an early stage and fairer hiring practices is the solution. We do not believe reverse discrimination [advocated by some](https://blogs.ams.org/inclusionexclusion/2017/05/11/get-out-the-way/) is the solution.

### 2020-01-22 index.tex
added excel

Pachter ends his review by saying ``under-represented minorities and
women routinely face discrimination and worse. This is completely
unacceptable.'' We agree. But we do not believe that the solution is to
allow for more diverse faculty regardless of their ability as
researchers. What we do believe is that increasing opportunities for
under represented minorities at an early stage and fairer hiring
practices is the solution, not reverse discrimination
\href{https://blogs.ams.org/inclusionexclusion/2017/05/11/get-out-the-way/}{advocated
by some}.

>>>>

Pachter ends his review by saying ``under-represented minorities and
women routinely face discrimination and worse. This is completely
unacceptable.'' We agree. We believe that increasing opportunities for
under represented minorities at an early stage and fairer hiring
practices is the solution. We do not believe reverse discrimination
\href{https://blogs.ams.org/inclusionexclusion/2017/05/11/get-out-the-way/}{advocated
by some} is the solution.
